\begin{frame}
\frametitle{Bachelor Degree}
\begin{itemize}
    \item The bachelor's degree is obtained after 4 years of study.
    \item The bachelor's degree is obtained after 240 credits.
    \item The bachelor's degree is obtained after defending the bachelor's thesis.
\end{itemize}
\end{frame}

\begin{frame}
\frametitle{What is the bachelor's thesis?}
The bachelor's thesis is a project that you need to do in the last year of study.

You need to:
\begin{itemize}
    \item Choose a professor who will guide you.
    \item Choose a theme and then a topic.
    \item Implement the project.
    \item Write 30-40 pages of documentation.
    \item Present your work in front of a commission.
\end{itemize}
\end{frame}

\begin{frame}
\frametitle{Bachelor thesis - How to choose a topic?}
 Choose a topic that you would  like to do. (you will work on it for at least 6 months)
    \begin{itemize}
        \item Your passion.
        \item Your hobby.
        \item Your favorite theme in the faculty.
        \item Your favorite professor.
    \end{itemize}
\end{frame}

\begin{frame}
    \frametitle{Bachelor thesis - How to choose a topic?}
    \begin{itemize}
        \item Choose a topic that you will be proud  of. (The only thing that will remain after you leave the university)
        \item Choose a topic that you will be able to finish.
        \item To increase your chances of getting into a master's program, choose a topic that is related to the master's program or conclude with a paper.
        \item If you work in a company, choose a topic from the company.
    \end{itemize}
\end{frame}

\begin{frame}
\frametitle{Bachelor thesis - How to choose a professor?}
\begin{itemize}
    \item Choose a professor that you like.
    \item Asked older students about the professors.
    \item Choose a professor that is related to the topic.
\end{itemize}
\end{frame}

\begin{frame}
\frametitle{Bachelor thesis - Where to find a topic?}
\begin{itemize}
    \item Choose from the university's site at \url{https://connect.upb.ro/propuneri}.
    \item Go to the professors and propose a topic.
    \item Go to the companies and propose a topic or get one from them.
\end{itemize}
\end{frame}

\begin{frame}
\frametitle{Bachelor thesis - Extra}
\begin{itemize}
    \item You can do the bachelor thesis in a team of students depending on the complexity.
    \item You can do the bachelor thesis with Erasmus+ internships.
    \item You can do the bachelor's thesis with any professor from the university or friendly university.
    \item Try to stay close to your domain of study. The commission at the end is formed from professors from your domain.
    \item You can write in English or Romanian.
    \item You can use any programming language or any tool.
    \item \textbf{You can do the bachelor thesis during the summer practice.}
\end{itemize}
\end{frame}

\begin{frame}
\frametitle{My proposals for bachelor thesis - Blockchain}
\begin{itemize}
    \item CuEVM - A new EVM implementation in cuda for Ethereum to run on GPUs. (Minh Ho (NUS))
    \item MECAnywhere - A cloud service through blockchain for using underused computational resources.
    \item Post Quantum Blockchain - A blockchain that uses post quantum cryptography.
    \item Post Quantum Wallet - A wallet that uses post quantum cryptography.
    \item Post Quantum ID - A blockchain based ID that uses post quantum cryptography. (Ioan Stan (Bitdefender))
    \item Blockchain High School Platform - A platform for high schools over blockchain for their websites. (Andreea Dobrita (SNSPA))
\end{itemize}
\end{frame}

\begin{frame}
\frametitle{My proposals for bachelor thesis - Quantum Networks and Quantum Computing}
\begin{itemize}
    \item Quantum Key Distribution Application - An application that uses QKD for secure communication. (Alin Popa)
    \item Quantum Entanglement  Network Simulator - A simulator for quantum entanglement networks. (Bogdan Ciobanu)
    \item Quantum Leader Election Benchmark - A benchmark for quantum leader election algorithms. (Daniel Lee (NUS))
\end{itemize}
\end{frame}

\begin{frame}
\frametitle{My proposals for bachelor thesis - Number Representation Systems}
\begin{itemize}
    \item Number Representation Systems Software Library (NRS-SL) - A library that implements all number representation systems.
    \item Number Representation Systems Hardware Library (NRS-HL) - A library that implements all number representation systems in hardware.
    \item Number Representation Systems Benchmark - A benchmark for number representation systems.
    \item Audio/Video Compression and Editing  using different Number Representation Systems. (Andrei Trasca)
    \item Artificial intelligence  using different Number Representation Systems. (Teodor Neacsu)
    \item Statistics Analysis using different Number Representation Systems. (Ebru Resul (Keysight))
\end{itemize}
\end{frame}

\begin{frame}
\frametitle{My proposals for bachelor thesis - Computer Architecture}
\begin{itemize}
    \item Microcod pipelined RISC-V - A microcode implementation for RISC-V in Verilog. (Nicolae Tapus)
    \item RISC-V simulator - A simulator for RISC-V. (Nicolae Tapus)
    \item Cold-Wallet - A hardware wallet for cryptocurrencies. (Rares Ifrim)
    \item RISC-V Zero-Knowledge Proof - A Zero-Knowledge Proof for RISC-V. (Rares Ifrim)
\end{itemize}
\end{frame}

\begin{frame}
\frametitle{My proposals for bachelor thesis - Robotics and Automotive}
\begin{itemize}
    \item Formula Student - A project for the Formula Student competition. (Alexandru Vaduva (Siemens))
    \item Automotive Security Emulator - An emulator for automotive security. (Alexandru Vaduva (Siemens))
    \item RONIN - A project to build robots. (Daniel Rosner)
    \item Humanoid Robots - Use humanoid robots in interaction with humans. (Adriana Tapus (IPP - ParisTech))
\end{itemize}
\end{frame}

\begin{frame}
\frametitle{Proposals for bachelor thesis - Not related to my interests}
\begin{itemize}
    \item Healthcare (Flavia Oprea)
    \item Contests Platform (Stefan Avram (Keysight/Acadnet))
    \item Federated Learning (Dan Badea (Bitdefender Ambassador))
    \item Machine Learning Security (Damian Monea (Crowdstrike))
    \item Machine Learning Privacy (Teodora Baluta (Georgia Tech)/Ana Maria Cretu (ETH))
    \item Formal Verification (Andreea Costea (Delft))
    \item Ethical Hacking (Florin Stancu / Radu Mantu / Mihai Chiroiu)
    \item Rust Programming Language (Alexandru Radovici (OxidOS))
    \item Computer Vision (Emilian Radoi)
    \item Natural Language Processing (Mihai Dascalu)
    \item Privacy Technologies (Razvan Rughinis)
\end{itemize}
\end{frame}