\begin{frame}
\frametitle{Mobility programs}
\begin{itemize}
    \item \href{https://acs.pub.ro/parteneriate/relatii-internationale/acorduri-erasmus/}{Erasmus Opportunities}.
    \item \href{https://acs.pub.ro/public/21-27-Mobilitate-Studiu-Eplus-UNIVERSITATI-PARTENERE-septembrie-2024.pdf}{Universities List}.
    \item \href{https://upb.ro/concurs-granturi-erasmus/}{Foreign Language Exams}.
\end{itemize}
\end{frame}

\begin{frame}
\frametitle{Documents}
\begin{itemize}
    \item Language certificate or Foreign Language Exam in UNSTPB.
    \item CV.
    \item Motivation letter.
    \item Transcript of records.
    \item ID card.
    \item Diploma/Awards (optional).
    \item GPA.
    \item \href{https://acs.pub.ro/public/Regulament_Mobilitati_ERASMUS_2024.pdf}{Erasmus UNSTPB Regulation}.
    \item ASC Contest.
\end{itemize}
\end{frame}

\begin{frame}
\frametitle{Type of mobilities}
\begin{itemize}
    \item Study (607/674/707) vs Placement (2 to 4 months 756/824/+250) vs Study-Placement mobilities.
    \item Short-term (5 to 30 days) vs Long-term mobility (2 to 10 months).
    \item Travel grant and green travel grant (train/bus/shared car).
\end{itemize}
\end{frame}

\begin{frame}
    \frametitle{Rank of the Universities - R1}
    \begin{itemize}
        \item Universitat Politecnica de Catalunya + Universidad Politecnica de Madrid (Spain)
        \item Ecole Normale Superieure de Cachan (ENS Cachan) + Universite Paris-Saclay (ParisTech) (France)
        \item Technische Universitat Wien (Austria)
        \item Universidade Nova de Lisboa (Portugal)
        \item Technische Universiteit Eindhoven + University of Twente (Netherlands)
        \item Technische Universitat Ilmenau (Germany)
        \item Aarhus University (Denmark)
        \item Istanbul Gelisim Universitesi (Turkey)
        \item Universita degli Studi di Roma "La Sapienza" + University of Padua (Italy)
        \item University of Nicosia (Cyprus)
    \end{itemize}
\end{frame}

\begin{frame}
    \frametitle{Rank of the Universities - R2}
    \begin{itemize}
        \item Institut National Polytechnique de Grenoble + Universite de Strasbourg + Sorbonne Universite (France)
        \item Universite de Mons (Belgium)
        \item Warsaw University of Technology (Poland)
        \item Universita degli Studi di Torino + Universita degli Studi di Milano-Bicocca (Italy)
        \item Universidade do Porto (Portugal)
        \item Universidad de Sevilla (Spain)
        \item Abo Akademi Universit (Finland)
        \item Budapest University of Technology and Economics (Hungary)
    \end{itemize}
\end{frame}

\begin{frame}
    \frametitle{Extra}
    \begin{itemize}
        \item Erasmus placements for summer practice and bachelor's thesis.
        \item Erasmus placements for relaxing.
    \end{itemize}
\end{frame}



