\begin{frame}
\frametitle{Summer Practice}
\begin{itemize}
    \item The summer practice is a mandatory activity for all students.
    \item It needs to take 360 hours (45 working days) between 22nd of June and 7th of September (last year).
\end{itemize}
\end{frame}

\begin{frame}
\frametitle{Where can I do my summer practice?}
\begin{enumerate}
    \item Companies who have an agreement with the university.
    \item International companies who don't have an agreement with the university.
    \item Research projects with professors.
    \item Summer schools.
    \item Erasmus+ internships.
    \item Companies who don't have an agreement with the university.
\end{enumerate}
\end{frame}

\begin{frame}
\frametitle{How to find a place for the summer practice?}
\begin{itemize}
    \item From the university's site at \url{https://connect.upb.ro/}.
    \item Erasmus+ internships have open calls \url{https://upb.ro/erasmus/mobilitate-de-plasament-upb/}.
    \item Stagii pe bune \url{https://www.stagiipebune.ro/}.
    \item You can find a company by yourself. (international \url{https://leetcode.com/})
\end{itemize}
\end{frame}

\begin{frame}
\frametitle{Necessary documents}
\begin{itemize}
    \item \url{https://acs.pub.ro/studenti/stagii-de-practica/}
    \item Convenție Cadru (company) sau Portofoliu de practică (research project).
    \item Caiet de practică. (what you did)
    \item Atestat / adeverința de practică. (evaluation)
    \item Protocol of collaboration  between the university and the company.
\end{itemize}
\end{frame}
